### 2025-02-04 Paper/computers&geosiciences/CAGEO_LaTeXTemplate-main/main_document.tex
revised

\begin{keywords}
Rock segmentation \sep U-Net\sep Convolutional Neural Networks \sep Rockfall\sep Volume Calculation\sep 3D Surface Area Calculation
\end{keywords}

@@

In the study conducted by \cite{Song2006AFF} in 2006, rock segmentation on Mars was performed to plan routes and determine landing areas. Texture-based image segmentation and edge-flow driven active contour has been developed. Wavelet based local transform, multi-resolution histograms, and inter-scale decision were combined and used for rock segmentation. As a result of the experiments, \cite{Song2006AFF} obtained reliable rock segmentation results.

@@

The trained model successfully detected rock blocks within the study area (Fig. \ref{fig:Figure7}). The boundaries of 3111 rocks of various sizes were determined and created as a vector file (.shp). This method is not recommended for smaller areas. Because sufficient training data cannot be created. In areas where there are several rock blocks, detection can also be done manually. 
Sometimes there may be distortions at the edges and corners of the image. This causes errors in rock block detection. Therefore, a larger area than the area where the rocks are located should be selected as the study area.

@@

This study has presented a reliable method for segmentation and volume/surface area calculations and has also directly contributed to engineering applications in terms of determining the physical properties of rock masses. The segmentation section of the study is recommended for terrains containing a lot of rock blocks. It is possible to detect rock blocks in a short time. In addition, this method can be used to automatically detect different types of terrain. Deep learning models usually require a large amount of data for training. A large amount of data can be generated with the Random Sampling method proposed in this study. Volume and 3D surface area algorithms can be used not only for rock blocks but also for any object on the field. These algorithms only require precise DEM data and object boundaries. For example, these calculations can be made for a single rock block. In these calculations, ground heights and object heights must be determined clearly. When determining the object boundaries, they should be extended towards the ground. If the boundaries only represent the object, the ground heights will not be considered, and the results will not be correct. In some cases, the model can draw the boundaries of the rock blocks narrower. In this case, this problem can be solved by adding buffers to the rock blocks.

>>>>

\begin{keywords}
Convolutional Neural Networks \sep 3D Surface Area Calculation \sep Volume Calculation\sep  Rock segmentation \sep  Rockfall\sep U-Net
\end{keywords}

@@

In the study conducted by \cite{Song2006AFF}, rock segmentation on Mars was performed to plan routes and determine landing areas. Texture-based image segmentation and edge-flow driven active contour has been developed. Wavelet based local transform, multi-resolution histograms, and inter-scale decision were combined and used for rock segmentation. As a result of the experiments, \cite{Song2006AFF} obtained reliable rock segmentation results.

@@

The trained model successfully detected rock blocks within the study area (Fig. \ref{fig:Figure7}). The boundaries of 3111 rocks of various sizes were determined and created as a vector file (.shp). This detection method is not recommended for smaller areas. Because sufficient training data cannot be created. In areas where there are several rock blocks, detection can also be done manually. 
Sometimes there may be distortions at the edges and corners of the image. This causes errors in rock block detection. Therefore, a larger area than the area where the rocks are located should be selected as the study area.

@@

This study has presented a reliable method for segmentation and volume/surface area calculations and has also directly contributed to engineering applications in terms of determining the physical properties of rock masses. The segmentation section of the study is recommended for terrains containing a lot of rock blocks. It is possible to detect rock blocks in a short time. In addition, this method can be used to automatically detect different types of terrain. This study requires DEM and orthophoto images obtained from the field. A region is selected and labelled objects in any GIS software for training the model. The following processes are carried out entirely with Python scripts.

Deep learning models usually require a large amount of data for training. A large amount of data can be generated with the Random Sampling method proposed in this study. Volume and 3D surface area algorithms can be used not only for rock blocks but also for any object on the field. These algorithms only require precise DEM data and object boundaries. For example, these calculations can be made for a single rock block. In these calculations, ground heights and object heights must be determined clearly. When determining the object boundaries, they should be extended towards the ground. If the boundaries only represent the object, the ground heights will not be considered, and the results will not be correct. In some cases, the model can draw the boundaries of the rock blocks narrower. In this case, this problem can be solved by adding buffers to the rock blocks.
